Regular singular Volterra equations on complex domains

### 2023-07-25 reg-sing-volterra.tex
Show that V is a contraction away from the origin

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{\textcolor{orange}{[Proof of main result]}}
\subsection{Overview}
\subsection{An approximate solution}
\subsubsection{Construction}
\subsubsection{Asymptotics}
\subsubsection{Image under $\softpart$}
\subsection{Finding spaces where $\volterra$ is a contraction}
In this section, we'll prove the following proposition.
\begin{prop}\label{get-contraction}
For each $\rho \in (\tau, \tau + \epsilon)$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda$, and may require $\Lambda \gg \lambda$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By \textcolor{orange}{[limit property]}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$. By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

For each $a \in \domain$, we have

@@

Now, suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that

@@

for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight-line path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.

@@

Since we set $\sigma < \rho$, this brings us halfway to proving that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$.

@@

%------------------------------------------------------------------------
\color{SteelBlue}
\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that

@@

\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi

@@

is an isometry. More generally,
\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
f & \mapsto \zeta^{-\delta} f
is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$. This reduces to the previous statement when $\rho = 0$. For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$. Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.

>>>>

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{\textcolor{orange}{[Proof of main result]}}
\subsection{Overview}
\subsection{An approximate solution}
\subsubsection{Construction}
\subsubsection{Asymptotics}
\subsubsection{Image under $\softpart$}
\subsection{Finding spaces where $\volterra$ is a contraction}
\subsubsection{Overview}
In this section, we'll prove the following proposition.
\begin{prop}\label{get-contraction}
For each $\rho \in (\tau, \tau + \epsilon)$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda$, and may require $\Lambda \gg \lambda$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By \textcolor{orange}{[limit property]}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$. By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

\subsubsection{First steps}\label{first-steps}
The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have

@@

What we do next depends on whether $a$ is in $\near$ or $\far$.
Suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that

@@

for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.

@@

Since we set $\sigma < \rho$, this brings us halfway to proving Proposition~\ref{get-contraction}.

@@

Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from \textcolor{orange}{[difference bound]} that we can find a constant $M$ for which
\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]
Let's again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$. Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.

@@

Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt. \]

We can make this bound as small as we want by increasing $\Lambda$. To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and of the integration separately. At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
\begin{align*}
\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda - \lambda)R} \int_0^{1/5} t^{\rho-1}\;dt \\
& = e^{-\frac{4}{5}(\Lambda - \lambda)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
\end{align*}
At the end, we instead use a worst-case estimate on $t^{1-\rho}$:
\begin{align*}
\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)R(1 - t)}\;dt \\
& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)R} \right] \\
& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}.
\end{align*}
\textcolor{ForestGreen}{[Consider just writing ``const.'' instead of explicit constants.]}

We now know that by setting $\Lambda > \lambda$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{get-contraction}.
%%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
%%\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]
%%This time, we'll use the parameterization $\zeta = s \frac{\zeta(a)}{|\zeta(a)|}$, with $s \in (0, |\zeta(a)|]$:
%%\begin{align*}
%%|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{|\zeta(a)|} \left(\frac{s}{|\zeta(a)|}\right)^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
%%\end{align*}
%------------------------------------------------------------------------
\color{SteelBlue}
\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi
\end{align*}
is an isometry. More generally,
\begin{align*}
\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
f & \mapsto \zeta^{-\delta} f
\end{align*}
is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$. This reduces to the previous statement when $\rho = 0$. For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$. Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
